Computation Issues

### 2020-09-29 README.Rmd
working on updating repo

0. [Objectives and Ideas]()
1. [Information on Hamby Data and Models]()
2. [Understanding LIME]()
3. [Applying LIME to Hamby Data]()
4. [Assessing LIME on Hamby Data]()
5. [Applying and Assessing LIME on Iris Data]()
6. [Notes on Readings]()
7. [Computational Issues]()
8. [LIME Applied to Logistic Regression]()
9. [Identifying `rtrees` Training Data]()
10. [LIME Variability Across Hamby Data and Models]()

>>>>

0. [Objectives and Ideas](https://goodekat.github.io/LIME-research-journals/journals/00-objectives_and_ideas/00-objectives_and_ideas.html)
1. [Information on Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/01-hamby_data_and_models/01-hamby_data_and_models.html)
2. [Understanding LIME](https://goodekat.github.io/LIME-research-journals/journals/02-understanding_lime/02-understanding_lime.html)
3. [Applying LIME to Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/03-applying_lime/03-applying_lime.html)
4. [Assessing LIME on Hamby Data](https://goodekat.github.io/LIME-research-journals/journals/04-assessing_lime/04-assessing_lime.html)
5. [Applying and Assessing LIME on Iris Data](https://goodekat.github.io/LIME-research-journals/journals/05-iris_comparison/05-iris_comparison.html)
6. [Notes on Readings](https://goodekat.github.io/LIME-research-journals/journals/06-literature_review/06-literature_review.html)
7. [Computational Issues](https://goodekat.github.io/LIME-research-journals/journals/07-computation_issues/07-computation_issues.html)
8. [LIME Applied to Logistic Regressions on Sine Data](https://goodekat.github.io/LIME-research-journals/journals/08-logistic_regression/08-logistic_regression.html)
9. [Identifying `rtrees` Training Data](https://goodekat.github.io/LIME-research-journals/journals/09-identifying-rtrees-training-data/09-identifying-rtrees-training-data.html)
10. [LIME Variability Across Hamby Data and Models](https://goodekat.github.io/LIME-research-journals/journals/10-LIME-hamby-variability/10-LIME-hamby-variability.html)

### 2020-09-29 journals/00-objectives_and_ideas/00-objectives_and_ideas.Rmd
working on updating repo

---
title: "Objectives and Ideas"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

>>>>

---
title: "Objectives and Ideas"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

### 2020-09-29 journals/03-applying_lime/03-applying_lime.Rmd
working on updating repo

---
title: "Applying lime to `rtrees`"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

>>>>

---
title: "Applying lime to `rtrees`"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

### 2020-09-29 journals/05-iris_comparison/05-iris_comparison.Rmd
finished organizing journals
working on updating repo

---
title: "Iris Comparison"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

>>>>

---
title: "Iris Comparison"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

### 2020-09-29 journals/06-literature_review/06-literature_review.Rmd
updates after meeting
working on updating repo

---
title: "Literature Review"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

@@

>>>>

---
title: "Literature Review"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---

@@

*Heike metioned that the sampling method they are doing is similar to what an SVM is doing.*

### 2020-09-29 journals/07-computation_issues/07-computation_issues.Rmd
working on updating repo

---
title: "Computation Issues"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

>>>>

---
title: "Computation Issues"
author: "Katherine Goode"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    theme: cerulean
    highlight: textmate
---
